---
title: "House Sales"
output: html_document
---

```{r}
library(ggmap)
sales  <- readRDS('data/01_corv_sales.rds')

corvallis <- c(lon = -123.2620, lat = 44.5646)
corvallis_map <- get_map(corvallis, zoom = 13, scale = 1, maptype = "satellite")
# Edit to display satellite map
ggmap(corvallis_map) +
  geom_point(aes(lon, lat, color = year_built), data = sales)

ggmap(corvallis_map) + 
  geom_point(aes(lon, lat), data = sales)

```
 
```{r}
corvallis_stamen <- get_map(corvallis, maptype = "toner", source = "stamen", zoom = 13)

ggmap(corvallis_stamen) + 
  geom_point(aes(lon, lat, color = year_built), data = sales)
```
 
# Base Layers

```{r}
ggmap(corvallis_stamen) + 
  geom_point(aes(lon, lat, color = year_built), data = sales)

# or

ggmap(corvallis_stamen, 
      base_layer = ggplot(sales, aes(lon, lat, color = year_built))) + 
  geom_point()

# so we can use facets

ggmap(corvallis_stamen, 
      base_layer = ggplot(sales, aes(lon, lat, color = year_built))) +
  geom_point() + 
facet_wrap(~class)
```

```{r}

```
Drawing polygons
A choropleth map describes a map where polygons are colored according to some variable. In the ward_sales data frame, you have information on the house sales summarised to the ward level. Your goal is to create a map where each ward is colored by one of your summaries: the number of sales or the average sales price.

In the data frame, each row describes one point on the boundary of a ward. The lon and lat variables describe its location and ward describes which ward it belongs to, but what are group and order?

Remember the two tricky things about polygons? An area may be described by more than one polygon and order matters. group is an identifier for a single polygon, but a ward may be composed of more than one polygon, so you would see more than one value of group for such a ward. order describes the order in which the points should be drawn to create the correct shapes.

```{r}
ward_sales <- readRDS('./data/01_corv_wards.rds')
head(ward_sales)
```
Add a geom_point() layer with the color aesthetic mapped to ward. How many wards are in Corvallis?
```{r}
ggplot(ward_sales, aes(lon, lat)) + 
  geom_point(aes(color = ward))
```

Add a geom_point() layer with the color aesthetic mapped to group. Can you see some wards that are described by more than one polygon?

```{r}
ggplot(ward_sales, aes(lon, lat)) + 
  geom_point(aes(color = group)) + 
  geom_path()
```

Finally, add a geom_polygon() layer with the fill aesthetic mapped to ward and the group aesthetic mapped to group.
```{r}
ggplot(ward_sales, aes(lon, lat)) + 
  geom_point(aes(color = group)) + 
  geom_polygon(aes(fill = ward))
```

Now that you understand drawing polygons, let's get your polygons on a map. Remember, you replace your ggplot() call with a ggmap() call and the original ggplot() call moves to the base_layer() argument, then you add your polygon layer as usual:

```{r}
ggmap(corvallis_stamen, 
      base_layer = ggplot(ward_sales, aes(lon, lat))) +
  geom_polygon(aes(group = group, fill = ward))
```

Uh oh, things don't look right. Wards 1, 3 and 8 look jaggardy and wrong. What's happened? Part of the ward boundaries are beyond the map boundary. Due to the default settings in ggmap(), any data off the map is dropped before plotting, so some polygon boundaries are dropped and when the remaining points are joined up you get the wrong shapes.


Don't worry, there is a solution: ggmap() provides some arguments to control this behaviour. Arguments extent = "normal" along with maprange = FALSE force the plot to use the data range rather than the map range to define the plotting boundaries.


```{r}
ggmap(corvallis_stamen, extent = "normal", maprange = FALSE,
      base_layer = ggplot(ward_sales, aes(lon, lat))) +
  geom_polygon(aes(group = group, fill = ward))
```

Now repeat the plot, but map fill to num_sales. How would you describe the pattern in the number of sales by ward?

```{r}
ggmap(corvallis_stamen, extent = "normal", maprange = FALSE,
      base_layer = ggplot(ward_sales, aes(lon, lat))) +
  geom_polygon(aes(group = group, fill = num_sales))
```

Repeat the plot again, but map fill to avg_price. Also, set alpha = 0.8 in your call to geom_polygon() to allow the map to show through.

```{r}
ggmap(corvallis_stamen, extent = "normal", maprange = FALSE,
      base_layer = ggplot(ward_sales, aes(lon, lat))) +
  geom_polygon(aes(group = group, fill = avg_price), alpha = 0.8)
```
The predicted house prices in preds are called raster data: you have a variable measured (or in this case predicted) at every location in a regular grid.

Looking at head(preds) in the console, you can see the lat values stepping up in intervals of about 0.002, as lon is constant. After 40 rows, lon increases by about 0.003, as lat runs through the same values. For each lat/lon location, you also have a predicted_price. You'll see later in Chapter 3, that a more useful way to think about (and store) this kind of data is in a matrix.

When data forms a regular grid, one approach to displaying it is as a heatmap. geom_tile() in ggplot2 draws a rectangle that is centered on each location that fills the space between it and the next location, in effect tiling the whole space. By mapping a variable to the fill aesthetic, you end up with a heatmap.
